Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

### 2018-03-02 manuscript.Rnw
Clean up sporo_PIC
Add Table 3 to manuscript

<<run_analyses, results="hide">>=
# set working directory, run all analyses, save results objects
setwd(here::here())
source(file = "bin/cont_phylosig.R")
source(file = "bin/binary_phylosig.R")
source(file = "bin/microclimate.R")
source(file = "bin/binaryPGLMM.R")
source(file = "bin/trait_PCA.R")
save(list = ls(all = TRUE), file= "results.RData")
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage

>>>>

<<run_analyses, results="hide">>=
# set working directory, run all analyses, save results objects
setwd(here::here())
source(file = "bin/microclimate.R")
source(file = "bin/trait_PCA.R")
source(file = "bin/cont_phylosig.R")
source(file = "bin/binary_phylosig.R")
source(file = "bin/sporo_PIC.R")
source(file = "bin/binaryPGLMM.R")
save(list = ls(all = TRUE), file= "results.RData")
@

@@

% Table 3
\clearpage

<<sporo_PIC, results="asis">>=
PIC.results <- round_df(PIC.results)
PIC.results <- embolden_p(PIC.results, col.select=c("pval"))

print(xtable(PIC.results,
             label="table:PIC_sporo",
             caption="Results of phylogenetically independent contrasts analysis of quantitative (sporophyte) traits related to epiphytic growth. All trait contrasts were made by subtracting epiphytic values from terrestrial values; thus, a positive contrast indicates greater values for terrestrial clades. Significant differences between epiphytes and terrestrial clades in bold."),
      sanitize.colnames.function = custom_cols,
      sanitize.rownames.function = custom_rows,
      sanitize.text.function = function (x) {x},
      include.rownames=TRUE,
      caption.placement="top")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%% Figures %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
